\input preamble



Of course, our atmospheric discussion has included terms of fidelity.
We may think of it as a study project or thought experiment in
preparation for conversation.  As it happens, some notes have become
due.

There's so many dimensions to the extents I can imagine generally.
I'm going to skip the stuff that's uninteresting and pedantic for me.
The points normal to conversation in my mind include the discussion of
the actions of others which may appear to interfere but which we
recognize and accept as independent of our concern.  

But then we entered into a serious review of the intimacies of
fidelity, where abstract activity may betray an abstract sense of
fidelity in the abstract languages of social intercourse.  This sense
developed the ethereal language of image as required of the
psychological commitment of an intimate relationship.

The nondeterministic equation of being is
$$\displaylines{ \psi = \alpha \times \beta \times \gamma, \cr
 \psi = \alpha + \beta + \gamma.}$$

where the psychological state of being of the individual, $\psi$, may
or may not include a degree of love or affection.  The terms $\alpha$,
$\beta$, and $\gamma$ represent the relationships of the individual to
itself, family and friends, and society respectively.  This
classification of representation, otherwise level of abstraction, is a
variable not represented beyond the semantic context within the
complexity and nondeterminism of mind and spirit.

In the context of intimacy,
$$
 \psi = \alpha \times \beta \times \gamma,
$$
love enters into and binds the self with another, the intimacies
of trust are essential to the preservation of self.  A violation of
the self as reachable from the partner would degrade the relationship
to one where the two individuals are independent as represented by
$$
 \psi = \alpha + \beta + \gamma.
$$
This form of individual psychology (being) is normal to regular social
and professional relationships.  Self preservation is assumed normal,
and the entanglement of self with others abnormal.  For some
individuals, this form of being is abnormal to an intimate
relationship.  

The firm establishment of such understandings in a committed intimate
relationship is central to the maintenance of trust.  How profound is
the expectation of trust for the preservation of the (exposure of the)
intimate self to the other.  

The next topic following becomes the discussion and repair of
perceived violations to the intimate self on behalf of the partner.
It is normal for these discussions to arise in the development of the
joining of the whole consciousness.  In these processes the methods
and habits of the understanding would develop as the relationship
develops within the joining of the whole consciousness of the couple.


\bye
