\input preamble

Work in Gerard's field supported the implementation of objectives from
other fields including planetary science, space flight science, and
stellar science.  For Gerard and the members of his community,
everything fell into one of these bins.  The planetary and planetoid
orbiters from the academy of fine arts were planetary science automata
from the perspective of the artificial orbital science community.  The
asteroid mining and communications infrastructure were stellar
science.  Gerard's interest was in delivering automatic systems for
the best realization and maintainence of those projects.  When a
science project expired, if it did, the implementation came under the
domain of the artificial orbital science community.  The abandoned
material was supported, repurposed, recycled, or disposed of as they
found prudent, necessary and expedient.  These tasks were handled by
public committees and their public participants, who proceeded through
the production and publication of letters and votes with each step of
each subject under their purview.  

With a radio telescope, terrestrial command and control was
nonexistent.  It was not, strictly speaking, necessary to the
operation of the perpetual stream systems in space.  The extent of the
deep space network would expand according to the progression of
centuries to provide its next milestone in extra solar bandwidth
facility.  

Interplanetary internet would need to be fit to each task, a far more
complex decision tree for the committees of the artificial orbital
science community to navigate.  The budget for these activities would
be displaced by the budgets for new activities while the radio
telescope was offline.  An admirable trait of his fellow human beings,
while entirely inconvenient to the members of his field -- excepting
himself.  Gerard and Sophie could repair and replace near field
interplanetary internet automata, and in a sense they were a program
counter on the community's cost and benefit computer.

\bye
