\input preamble-pdf

The water was like the air, still and chill and breathable.  From my
perch over the surface I could look into the glass, or over the
atmosphere, as I cast my plastic minnow into the lake.  The water had
a brownish color to it, from the trees they say.  Many oaks and pines
and maples in Canada.  The deep waters held in mountainous rocky
crevaces purified the sense of health and wealth and body and mind.
The spirit flew over the tranquility of the moment as I sat there, a
boy alone in my grandfather's very nice little dingy, fishing.  I
could care less if I caught one, or not, excepting the grip held of
a boy's sense of the expectations of others.

He followed the simulated minnow I was reeling toward me.  All I saw
of him was one brilliant moment.  Transfixed by the drama of it.  The
fish came up from underneath the line of the minnow, just before it
broke the surface.  He turned at the sight of me and disappeared into
his depths as quickly as he appeared, his flanks lit in the diffuse
light of an atmospheric morning like a parade float.  Flashed to
memory by beauty and grace and substance and significance.

I wanted to eat that fish.  I still want to eat that fish.  Not
literally, of course.  That would be weird.  He's beautiful.  Big.
Meaning old.  The big, old fish stuffed and mounted over the mantle in
the dining hall nearby the constant reminder of their majesty and
dignity.  

The fish have a body and a mind.  No matter their consciousness, it is
the {\it animus} that contributes to my sense of the world.  And
therefore my consciousness obligates me to thank the fish, and all
fish, for the sacrifice of their mind-body identity to my daily
sustenance.

Did that fish, on that day, speak of more than ``I'm not eating
that''.  Did he realize only so late in the fetch of that minnow that
it was the plastic lure of a predator.  Perhaps.  It's plainly
possible.  And being possible, the simplest explanation.  And the
simplest explanation, the best explanation.

Or did that fish, on that day, say ``I see you'', and in that
expression oppose my intent to catch him, and in that opposition curse
his predator.

\bye
