\input preamble

Sophie returned to her apartment full of her respect and admiration
and now full bloom love for him.  She did not think of children.  She
thought of the feelings she had for a mate, the promise of a couple,
and wondered again at the mystery of this life that we are so drawn to
each other as to love and fight continuously if not for the maturities
of self awareness.  If fighting and conflict are ultimately
expressions of ignorance, and love an expression of our genetic
origins and evolutions, then could we not escape love as we endeavor
to escape conflict in order to move ourselves forward through time.
At least that's a hyper-rational graduate student perspective.  Not
satisfying.  Why would I try to oppose what I am when the problem I'm
trying to solve is how to get more work done.  Sophie felt relieved at
the reception she enjoyed with Gerard, but lived in another situation.
She was still climbing the mountain that Gerard had climbed.  She
struggled with the intellectual muscle as all students do.  She knew
that she was going through an experience of growth that would deliver
her to the possession of strength.  That had nothing to do with her
feelings for Gerard.  She had seen him, had gained interest and found
out who he was, and then eventually her interest grew to feelings of
admiration and the precipace of love that she had to face before she
went mad with it.  She had tried to avoid it, to put it aside for a
more convenient moment, but the feelings ate at her ability to get
work done.  Appropriately enough, from her perspective, she went to
see him during his office hours to place her bet and get a response.
To realize the problem and in this way to deal with it.  To go through
it rather than around or over or under it.  The success she met with
blew open a hole in her breast and let it out.  It was now a whole new
problem, but one that Gerard would understand.  She found the courage
or the will to put together something to eat and to get enough work
done that she could retire to sleep.

\bye
