\input preamble

It is unfortunate that the Constitution of the United States has a
hole in it.  It is also unfortunate that economic leisure has a dark
side.  I never imagined someone so weak as to be consumed by power or
money, but in a particular sense I am one of the people who never
travelled more than twenty miles from the place of his birth.  

We have the example of the Koch brothers and the lust for power that
produced a string of infamous tragedies and misspent billions of
dollars.  Some are myopic, but the example of the Koch brothers and
their ``dirty dozen'' claim to absolute power for money defies the
conventional American experience as well as economic theories of
behavior and leisure.  

The myopia of greed produced the hole in the Constitution, and
produces the politics of hate.  In this case, the Government of the
United States is no more than a source of wealth.  And in this case
the offense perpetrated by the myopia of greed is theft and betrayal
and treason.  

That voters and representatives pursue politics as a contest for the
disposition of our common and collective resources is a vaguely
tolerable extremity of pettyness, but when that pursuit becomes a
direct challenge to the Constitution and Government of the country it
is treason.

It is a boon to international politics, in particular Russian foreign
affairs.  The Russians enjoy their particular brand of craziness, and
perhaps we can be generous enough to be grateful for their continuous
pleasure in pointing out the similarities with our own because we have
a low tolerance for insanity.  Strategically a stable United States is
in the global self interest of the economies with enough advancement
to depend on our financial markets.  And in this perspective Russian
antagonism serves us in pointing a finger at the strategic
instabilities caused by that case of treason.

\bye
