\input preamble

\bf Interaction in two halves of a nutshell

\bigskip

\rm

Inspecting the problem of interaction is essential to resolving a
model of computing as employed for language or system or application
development.  Turing's Choice Machine is interesting for its
mathematical crispness, but not as pragmatic as desired until
abstracted to include the quasi-deterministic node with multiple
threads or processes.  The thread - process, network, and user
interface each represent the classic domain of the interaction
problem.

The objective challenge faced here is to encompass or contain the
interaction problem faced by designers and implementors on
conventional and unconventional hardware.  I submit that this is
accomplished with the two hemispheres of {\it synchronous} and {\it
asynchronous} processing.  That any problem of conception or solution
is best facilitated from this point of origination.  Furthermore, that
the simplicity of this toolset delivers power and facilitates
discipline.

\medskip

{\bf Synchronous Processing}

\medskip

In the synchronous case, the processing of input from the interactor
is immediate and produces any output to the interactor.  This is the
trivial case from the science and engineering perspective.  It poses
no challenge accepting the presumed process I/O facility.  The
immediate processing of input for output is otherwise known as the
{\it deterministic} processing of input and output.

\medskip

{\bf Asynchronous Processing}

\medskip

In the asynchronous case, the processing of input from the interactor
to produce output to the interactor is {\it nondeterministic}.  The
{\it ordering} of input and output is a design objective.  An example
of {\it unordered} I/O includes the graphical user interface in the
case of high frequency output ({\it e.g.} 3D, VR, gaming) where the
threads are prioritized to deliver the best achievable quality of
experience.  An example of {\it ordered} I/O includes a store and
forward network where input is stored for subsequent processing which
determines output.

\medskip

{\bf Conclusion}

\medskip

This inspection of the interaction problem covers the experience of
the writer in identifying and characterizing interaction problems in
practice.  Academic notes and comments on the problem described here
are most welcome via email or twitter.

\bigskip

{\it John Pritchard}

{\tt http://twitter.com/syntelos}

{\tt mailto:jdp@syntelos.com}

\bye
