\input preamble

Imagine it.  A president on the fone, a space craft in orbit around
the Moon, reality undone on the ground and in the air.  The asteroids
and spaces demanding, insaning, waving and raving.  The candy raving
sex crazy was so dark and confused.  There was every kind of madness
at home and in the street.  On the block.  A passport stolen.  Tools
stolen.  Further incursions to measure and weigh.  How to employ the
tools to manage it all in three dimensional interactive hypertext.
The blind messaging.  Eventually she collapsed, Geraldine.  She gave
in.  She kicked me out using that insane tool.  Psychology Today
kicked me out using that big, dirty tool.  Ignore him, he's nuts.  Oh,
yea, that's professional.  Familiar with that domain?  Once, and then
again.  A true pit.  ``He's committed.''  With locks on the gates.
What's in a word?  ``Are you doing this voluntarily?''  ``No!''  ``Too
bad!''

With nary a clue he climbed and climbed over every rock he could find,
blind, or very nearly so.  He had a narrative.  He had a tool.  ``You
won't know who to trust.''  ``I trust Barack.''  ``Do you trust
Michelle?''  ``Of course''.  ``Send Michelle when you're talking to
me.''

The Flight of the Intruder done a thousand ways.  The Sound of Music
done a million ways.  ``They see Indiana Jones.''  ``Yea, I see
that.''  ``Need a lift.''  ``Pages.''  ``Not sure how to step this
thing forward that way.''  ``You'll find it, I've placed our faith in
you.''

The naval pier would drop bombs on it.  O-B-A-M-A.  The peers would go
mad with it.  O-B-A-M-A.  ``We're on your truck.''  Every day.

And here we are.  The original story line meets our {\it ex post
facto} romantic story line.

\bye
