\input preamble

What do I need to know.  I wake up and review memory and abstraction.
From here King's Highway -- a most magnificent piece of history --
looks like Kate Middleton.  And the grace of kindness looks like
space.  Not cosmos but interiors.  Places of capacity lift and promote
consciousness following the principles of airport architecture.

Was it betrayal?  Love, angst, jealosy, confusion, hate, and anger?
In this position it seems to accumulate to destruction, whatever it
is.  And whatever it is would quickly become less interesting than the
attention.  

Once again I place my faith in sanity.  I am the instrument.  I am the
experimental stimulus.  Hope I live through it.  After all, I live in
a world where people still believe in some pretty terrible things.

Which contrasts to the observer.  Oh, boy.  That pisses em off.  Don't
look at em, they'll come after you with everything they've got.  No
joke.  Everything they've got.  Fuckers.  Lazy, ignorant,
superstitious animals.

Not unlike the creature sitting in front of me.  His skin the color of
dirt.  It's not drugs.  He has no social contact.  It's absence.  He's
not dressed warm enough to not be terribly frozen.  His posture
suggests contentment.  He stares off across the space before us.  He
collects himself and reminds me of another example of the self
satisfied character.  And appears another.  Dressed well for Miami.
He fits in.  Congratulations: you've solved the problem.  Don't exist.
Deny the self that jealosy, envy and greed starve their eyeballs.

The counter argument poses them as beggars and thieves.  Tripe.  All
y'all are variations on that theme and you know it!  The loss of art
that brings credit card to cash register to form a transaction for
food doesn't absolve you of your sins.  

Loathsome creatures, the uneducated, ungrateful, proud and fearful and
arrogant.  The space to evolve more important than sorting my
nightmares, I'll put this away.

\bye
