\input preamble

The arm, $\kappa\varepsilon\alpha$, was a serious code.  The kappa, \
$\kappa$, was the faith and confidence of the United States.  The
epsilon, $\varepsilon$, was the epistemo-logical network including two
families of four members who maintained that confidence.  The alpha, \
$\alpha$, was the best I got.  If not consciousness then consistency
of consciousness.  Education.  Scholarship.  Research.  Development.

Microscopes and telescopes employed on tangents to preserve the
integrity of $\kappa\varepsilon\alpha$.  Hence,
$\kappa\varepsilon\alpha \iota\kappa\varepsilon\alpha$.  And the
entertainment.  A thin allusion that cracks my ribs.  ``Oh, my, this
is the best version of the CIA WETDREAM.''.

And this.  Walking away from such ethereal acrobatics knowing that
there was no further entanglement of my greek user interface and the
worlds of intelligence agencies and their governments.

These two families of four, {\it Pritchard} and {\it Obama}, intact in
their respective r\^oles and responsibilities and integrities.

Love the Coopers.  The finitude.  The challenge.  How to fly this
airplane home to safety.  A ship to weather any storm.  

A bit too well made.  But I am not breaking a mast in a wind, or
loosing a rudder on sand.  Absolument pas.

Batou hit the tank again with his high mass mag rifle.  Major Kusanagi
marshalled the dust mites to scower the floors of all doubt.  This is
me.  This is us.  This is real.  I'm beyond in love with you.  That
print is immortal ink.

\bye
