\input preamble

Sitting on a table in an open, heated commercial space where my day
proceeds with all the vigor of sorting clothes and smoking the
occasional cigarette, my heart is beating out the rhythm of a kind of
panic.  It is not the panic of loss, but the stress of a love
untethered by knowing.  It's force is heavy like the rage of a storm,
but it is only love.  The love this man feels for the woman who boils
him like a frog with the depth of her intentions and commitment and
love for him.  He knows that love by pain and stress and the
psychological disorder that accompanies any moment without her,
according to what internal rhythms he will never fathom.  Only the
passing of time that brings his state to its next high, and the
passing of time that will bring her can comfort him.  Plainly he is
destitute in it.  That such commitment and passion as crush him, a
mountain, into grains fine as sand were possible he never would have
imagined.  She finds every power available to impress upon him, to
emboss into the texture of his soul, each faith required to follow her
into her world of faith and faithlessness where olympians vie for the
glories of expression and realization and art.

At least, this he finds among the rubble that remains of his mind.
Long lost to his commitments.  His head in a bucket tied to his belt.
How he could survive such stresses and see her holding the keys and
still love her only increasingly so the mystery.  But love her
increasingly with proportion to the destruction promised by his inner
consciousness he does.  He's uncertain whether she realizes the
effect.  Certainly she has some idea.  But could anyone understand
such a thing were possible unless someone who experiences it wrote of
it.

\bye
