\input preamble

The government of society is first concerned with economics in the
sense that politics and economics have a relationship that we can
identify in the character of the constitutional faults in our
experiment in self government -- the United States.

Advantage and the myopia of daily life -- micro economics -- at odds
with fairness within the analg computer of real life.  The level
playing field is a substantial and important metaphor.  It represents
a principle of establishment and foundation.  Why have we formed this
union if not our own self government, and if not for our own self
government the for our self exploitation.  In this, latter case we
have data from every century in the modern era.  Empires collapse as
imbalanced social orders of organization and unsustainable economic
models.

It is true that the long view would reach into microeconomics to
stablize a fixed income dependent.  That is, this and the other cases
of implication are important.

It is for these reasons that the long view differs from the immediate
view.  That safety and security and sustainability are well within
reach on a carefully chosen walk in government and politics.  The
course of this walk is to balance trades acrss actuality and spirit.
To produce the best available results for everyone.

The Hippocratic Oath says do no harm.  A government and politics
founded on these principles makes painstakingly plain notes on its
exceptions.  And in every case the fair participants walk away from
each case activity blessed.

\bye
