\input preamble

The New Testament of the Bible is led by the manifesto of a militant
reaction to the experience of Jesus of Nazareth.  It is nothing if not
adult, historiographic, and militant.  In a lighter sense, it could be
described as payback written by unknown authors ({\it i.e.} ``Titus'')
lost to (the record of) history.  The ways and means enumerated within
are clear and concise.  And the realization in two thousand years of
actuality proportional to its varied message.  These are the voices of
the enemies of empire and power projecting the power of humanity onto
the backs of the wretched with salvation in army.

There's plenty to agree with, here.  My own experience in these United
States is possessed of a striking similarity (from a very abstract,
sociological perspective).  I think Jesus was a very smart man who,
like Buddha, dove into life with the entirety of his force.  He was
loved and hated and destroyed.  That the record we have was not begun
until a century later is an historical testament to the actuality of
his moment.  His followers were beside themselves for a generation or
more, and the followers of his followers eventually cooled off enough
to launch the greatest war in human history (but one possible reading
of events).  A two thousand year war against arrogance, self
righteousness, power and greed and the salvation of it available
through the peace and love of humanity.

That the words peace and love should still light fires of arrogance
and self righteousness, hatred and frustration today the proof of
verity within.

From the vantage point of two thousand years it seems self evident
that peace and love are the enduring truths of the message that remain
at the heights of scholarship and humanity available today.  The
realization of the actuality promised by the ``war of the sacrifice''
remains scattered, divided by the same sense of division of two
thousand years ago in the moment of the writing of the New Testament.
It's long past time to realize the meaning of the most basic facts
available to us in history.

\bye
