\input preamble

Elizabeth in succinct form came to me when I was talking with John.

He was describing his brief, harried experiences in New York City.  We
were making jokes about our perspectives.  As NYC newbs he was a
potatoe and I was a mouse.  He knew nothing and I knew something on
our first excursions into that grand canyon.  He called himself naive.

I said that it was a terrible pretence to call that naive.  He didn't
know it, didn't know it existed (in a particular sense).  He went
there, saw it, and might as well have reacted as I did on seeing
Asheville.  Oh, wow, that exists.  

The idea that the lifestyles of our leaders are unhealthy is
challenging in a similar way.  If we acccept a peaceful indigenous
primitive (or similar) lifestyle as healthy and the urbane lifestyle
of those surrounded by their own delegates and adjuncts as unhealthy,
then we can replace ``healthy'' by binary variables representing the
hypothesis.

The argument against might employ the necessity of leadership and
conclude with a false comparison between necessity and healthy.
Alternatively one could elect to attack the proposed model or
spectrum, but that's just avoiding the debate -- not substantial to
the general concept proposed.  Obviously health exists in a spectrum,
field or manifold.

The argument in favor elaborates on spiritual and psychological health
and the deficits of a false realism for the individual, one that
provides too little and costs too much.  The novelty is applying this
basic concept to the monarch in context, where we tend to demure to
the very same false realism that is unhealthy for the very same
reason, an irrelevant sense of necessity.

If we can recognize things like this, our subliminal false realisms,
we'll all be much healthier.  It's not because leadership is necessary
that the r\^ole is healthy for the leader or the follower.  In brief,
the world is so full of analogous examples that the actions of a
monarch to recognize these issues have a very broad latitude,
including her own retirement.

\bye
