\input preamble

My experience of this world would ruin my sense of love and
compassion.  The collective consciousness digs a dialectic that
submerges sex regularly, periodically.  At points, dives into
collective delusion.  

At this scale it is neither compassionate nor fancy, but hypocritical
and puritanical.  

An example of the kind could be taken from ``no sex in public please,
we can't handle it -- bad things happen -- rogue males commit
atrocities''.  In this case, what we have labelled ``rape culture''
could be seen as the process of dealing with our situation.

While the representation of ``dark'' included sex and money and
business and inccluded some scary corners, it might as well represent
human natural meanings from nocturnes to erotica.  

We might as well lay out some modulation, interact with it, and raise
consciousness of the facts.  That we write on our bodies with
injustice when we speak of ourselves without respect.  That the male
sex is partially regarded with loathing, and that virtually all sexual
stimulii are focused on the female member of the species.

There is an obvious lack of cultural sexual balance that results or
contributes to apparent symptoms of such imbalances.  That is -- there
are obvious and vital associations or relationships between individual
and cultural issues surrounding and involving sex and consciousness.

In the world we see the fantasy sexuale of men of a certain age, and
eventually responses from young women affected.  The reptilian
background has had depth profond.  From sex to money to power.

To capture and describe it socially was a trick.  We enshrouded and
cloaked it with temporal action that captured the reptilian camoflage
of the thing.  We soaked this in color, and unveiled it in stages that
permitted it to breathe and evolve.  We employed reflection to spell
fire and ice treatments that illuminated the problem and suggested a
few remedies in concert with a world that participated in media
diverse and conversation public.  We did work on the subjects of image
and identity and appearance and discipline that acted to correct
imbalances on the cultural and social levels of this world.

The activity of reflection performed socially and in media has brought
profound change into our society.  We handle media with more facility
and responsibility, and we handle ourselves with greater fidelity of
self and country.

\bye
