\input preamble

Sophie woke to a swarm of flying lights modeled after bumblebees, the
result of her master's thesis in molecular fabrication: the
reproduction of organic mechanical techniques involving flight at low
reynold's numbers.  She had designed a particularly complex and
challenging thesis project that covered a number of relatively novel
materials and compositions with a demonstration objective that
declared a certain passion for the work.  The bees collected energy
from the environment and had a flight ceiling more than hundreds of
meters.  The microcosm of the project had fascinated Sophie, although
it was not as exciting as an ultralight that could fly to space and
return to earth in an organic cycle.  That was the primary objective
of her doctoral thesis.  If she couldn't complete that objective in
reasonable time, she would pick up the parts remaining and report on
that.  If she could complete it, her novel term ``organic cycle'' and
its definition excited her most.  This morning she woke to see some
new colors.  She had built them with encephalographic sensors
following some work she found on the subject.  It was just the kind of
tangent that made the work fun.  Her eyes focused on the colors and
remembered Gerard.  The lights told her conscious mind what her
subconscious mind was thinking.  She was in love.  The evolution in
the colors told her she was waking up, and so she got out of bed and
made some coffee.  Many hours to go before meeting Gerard at Lucia's
tonight.  She'd be back to shower before then, so there was no need to
think about what she would wear.  Anything would do.  She was
generally functional despite being more emotional than normal.  The
bumblebees were programmed to not go out the front door, and in her
absence to rest where they maximized energy collection.  She recalled
the plan to diversify their behavio, and the fact that that objective
had not yet reached the top of her priority stack.  She headed out the
door with everything she needed in a shoulder bag, and would not
return till dark.

\bye
