\input preamble

Two models come to mind for the state of sexual ignorance today.  One
is exploitation, and the other protection.  A comedy with sexually
transmitted disease is a case for the defence of sexual ignorance.  A
tragedy with sexual supply and demand is another case for the defence
of sexual ignorance.  Neither is sensible.  

Silence and ignorance are indefensible.  If there's one thing true of
the homo sapien it is that it wants to know.  This is the force one
should employ with any problem with a population of these creatures.

Knowledge is your power.  A lack of knowledge is someone else's power.
This is true for sex like anything else.

What goes on elsewhere.  Everyone wants to know the habits of others.
It gets funny.  I enjoy the seeing, and popping it open with the
injection of my own sense of the order of things.  As usual, the
number one unspoken subject is sex.  Are they having casual sex.  Are
they having sadistic sex.  Are they having romantic sex.  In my
perspective, this quiet despair for knowledge of others as our greater
selves is a bit weird.  At least awkward.  

There's a lot of social status involved.  A partner is a status
symbol.  The kind of relationship is significant.  Of course, in the
vanity fair, everything is significant to social status.  Social
status is the thing.  

Those of us with a large degree of sexual restraint built into our
characters are regarded highly, and others want to emulate the image
of natural electric beauty that sexual retraint has been clothed in.
Age old social defense from STDs plays a large r\^ole.  

Social defense and status merge in sex.  The forces of sexual demand,
status, defense, and exploitation are huge currents that have been
feeding silence and ignorance.  

Silence and ignorance are social ills.  Silence and ignorance of sex
for the homo sapien more than a bit ridiculous.

\bye
