\input preamble

A construction automaton had network interfaces by Gerard and a number
of necessities of structure and architecture by Sophie.  The
construction automaton pulled materials from the asteroid belt and
flew it into orbits established and updated by the AOS STCC.  The AOS
STCC was a closed self organized group.  As the AOS formed around the
facility and capacity to realize generalized artificial space flight
in self reproducing automata, a governance committee formed to
delegate topics to its charters.  This behavior on behalf of the
scientific community reflected the fact that collaboration from the
center of the field would be necessary to the development of molecular
fabrication technologies.  This perspective was widely recognized as
natural and sensible, trustworthy and worthwhile, and therefore the
natural course of self government for individual and society alike.

The construction network was slow, its strengths in communication
limited by distance and leveraged over its delivery of perpetual
income streams.  This wealth was allocated by the construction system
that other members of the community developed.  It maintained an
ecosystem that fed into the economy of the Sol system at established
devices of necessity of government.  The artificial orbital community
allocated resources to itself in the development of the Sol system for
the long term -- as afforded by the situation over term.  Inwardly AOS
were strategy poor.  Interplanetary comnunications support was
produced by other sectors of society for their own needs and
objectives.  Interplanetary internetworking for the AOSC could be
rather limited while the STC was advancing outward.  It was a truth
that told the story of the public good to be derived from the STC,
about the public good derived from space and its longer points of
concern, but left Sophie and Gerard to fend for themselves in their
individual existence and to repair, recycle, repurpose and develop
resources accumulated by the AOSC for their interplanetary and
interpersonal internetworking.

\bye
