\input preamble

Gerard saw Sophie staring out the window and wondered if she was
thinking about the moon.  There was a moment, there, that seemed to be
arriving.  They could and they should return to the moon.  It was so
peaceful, there, in solitude.  He could stay longer than Sophie's wave
rider could, and thought of a larger ship.  The work sheets for
budgets he produced said a couple things to him.  First that he would
need a more substantial income stream, and second that the size class
proposed a prohibitive parking arrangement.  It wasn't obvious how
four pylons for one ship was a public good.  He thought it over again.
That he believed the supporting argument to be the arbitrary
difference between one or two or three or four pylons.  The pylon grid
on equilateral triangles provided space and convenience and
established the ``one'', ``two'', ``three'', or ``four'' gridding
classses.  But building and keeping a ``four'' class ship in Foggy
Bottom would raise plenty of discussion.  The counter claim held a
unit's privacy and a share's economy.  Taking multiple spaces long
term would cost a share of the ship, credited to the community in some
sense.  His income plan was a community contribution, but as it
produced the income to support the ship, the application of the
benefit to closing the share would appear to be double counting the
thing.  Making distinct the community cost and benefits of pylon space
to voices on behalf of relatively aggressive precedent and practice
for sharing arrangements would be a matter of politics.  His living
arrangements were not an issue.  The allocation of pylons were an
issue.

\bye
