\input preamble

In the last hours before sunrise Gerard and Sophie were speaking of
their hearts' desires.  To return to space flight with the plan that
accomplished both a return to the moon and the best they could do for
AOS resources.  They would rendezvous with two birds in low earth
orbit, make the big swing through cislunar space, and then meet each
of the three AOS birds in lunar orbit that required periodic
refueling.  Each bird would get the full attention of an automatic
mechanic that would trade its time and materials and energy budget for
the health and well being of the subject automaton.  Any depletable
resources would be replenished, damage and fatigue would be repaired,
and then engineering requests for modifications and updates would be
processed according to opportunity.  The schedule of events derived
from the flight scenario would deliver one hundred percent successs
for each of the five rendezvous.  This contribution was not a
hardship, it was all fairly easily done with conventional technology,
but nonetheless it filled them with the joy of accomplishment that
they knew would be shared by everyone concerned with the ways and
means of doing the work of artificial orbital science.  Communications
to the array of sensors and systems on the lunar far side would be
improved by two hundred percent, and then the effectiveness of the AOS
presence in LEO would be improved by ten percent.  The moon was an
obscure point for many, and the center of the universe for some.  The
radio quiet and mass and proximity of the far side location made it
practical for many objectives.  The vary large radio telescope
measured tens of kilometers in diameter, was etched into the surface,
and could be seen from orbit.  The AOS provided communications links
for principal research access.  That it was very nearly offline,
otherwise, a source of great concern for those fields dependent on the
data it provided.

\bye
