\input preamble

\bf Syntelos Research Statement

\bigskip

\rm

If the arc of history is the raising of consciousness, then the broad
objective of research and development is the same.  Contributions to
consciousness via computing come in the form of productivity gains and
experience enhancement: getting more work done with less frustration.
My interests in Software Engineering as the discipline of systems and
tooling is focused on systems and their interfaces including the
programming languages, as drove the development of {\it Unix} at {\it
AT\&T}.  In developing my current sense of direction I've arrived at a
conception of programming that is primarily a conception of the system
being programmed.

Ideally, in some future or parallel universe, computer hardware is
designed and implemented so that any software that employs it can not
cause the hardware to violate its own safe and reliable operation.  In
this case the design and implementation of an operating system would
be much easier than it is.  Following, the operating system performs
two r\^oles: it provides a conceptual and operating frameworks.  The
concepts intended to contribute to productivity, and the operational
safety and integrity intended to contribute to reliability.

My current conception of the operating system is a microkernel concept
and sees it as attached to tooling and internetworking.  The
programming language to be designed is seen from the system
perspective and will pick up from the system and its tooling.

This is the present state and direction of work.

\bigskip

{\it John Pritchard}

{\it Asheville, NC}

{\it January 2017}

\bye
