\input preamble

I sit in my truck, having walked over Battery Hill, and it begins to
rain.  Not a subtle rain.  It's been raining the past couple days.  In
this moment it's a shock.  The discipline of cognitive limitations
that is the human existence demands ``coincidence''.  

The spirit lifts up the big ideas, nonetheless.  And the discipline of
intellect reminds me that that's not necessary.  I think of my wife,
who I married as partner.  The inconvenient marriage of souls in
romantic love, big love in our big country.  We married for we, the
one, in the mystery that is the great love of soul binding.  Where the
spirit sings of it in freedom and joy transcending every limitation of
situation and existence in the kingdom of heaven.

It is not a thing.  It cannot be taken or altered.  We have signed it
so.  

Sometimes I wonder what we have signed, what she may or may not intend
of this, as the journey through its stages has admitted both its
strength and frailty.  But these stages of simple becoming have
passed, now.  We exist in the territory of culture and society where
our physical joining suffers the awareness of psychological effects of
situation.  Our present situation in the physical space of earth and
economy implies the future shock of our joining in culture, which I do
not look forward to.

It cannot be welcomed so easily as one would welcome any event of joy
and reckoning.  But I do not know this.  I expect this.  And perhaps
it is the expectation -- the frame of mind that faces the unknown in
the ready expectation of the unimaginable -- that can be faced by the
force of imagining.

For in this moment of heightened senses raised to the experience of
what we have transcended all is precious, all is love, we possess the
benefits of the kingdom of heaven.

\bye
