\input preamble

\bf Syntelos Research Statement

\bigskip

\rm

In my research I've realized the potential for beginning from the
desired premises, regardless of the appearance of possibility.  I
apply the courage of exploration and the discipline of pursuit to that
which I find interesting and worthwhile in the current state of
science and engineering as I'm aware of it.

The frontiers of computing remain in the interactive spaces of
internetworking where the force and freedom of the individual meets
science and society.  The realization of the individual is at risk in
the politics and culture that appear to weigh the individual against
the awareness of the right to peace, liberty, and the pursuit of
happiness.  The development of knowledge and technology, indeed
productivity and creativity, depend on the personal sense of security
that would be infiltrated or manipulated by the darkness of
socio-economic doubt.  My contribution is at least the displacement of
the doubts, and ideally the facility to produce and create with
greater convenience and utility.  To promote the power of the
individual on the internet regardless of the socio-economic
environment, in this way preserving the promise of freedom represented
by the over-arching history of human consciousness.  

To this end I will continue my work in the domain of computer
programming languages and systems specialized to the capacities of
internetworking.

\bigskip

{\it John Pritchard}

{\it Asheville, NC}

{\it January 2017}

\bye
