\input preamble

Have you studied psychology?  Gerard asked Sophie.  He had her name,
and they were returning to a state of consciousness that facilitated
the satisfaction of the need to talk, to converse and in this way to
interact intellectually.  That next drop of the existence of Gerard
and Sophie.  They each recognized that this was already far beyond
getting a name and address.  He had no address for her and didn't
think of it.  A subconscious thought of contacting her in future was
displaced by a subliminal reaching for not letting her get away.  

Yes, some.  She replied.  I enjoy Gefou's conception of psychology as
representative of the acquisition of character independent of the
architecture of society that defines normal, and relegates the
remainder to anthropolgy.

Well, ok.  Gerard smiled.  He was struck.  Shot down like an amateur
caught in front of an ace.  Guess we're done with psychology.  And the
word comprehension?

Comprehension?

Same idea.  More fun as the acquisition of character that engages like
an envelope or container rather than a meeting or overwhelming.  

Ah.  Right.  Cool.  Sophie paused to reflect on the whole.  Wild.  

The fighter pilot analogy fit to the age of missles and jets when the
duration of the affair was constructed around the time of flight of a
supersonic missle.  The analogy failed at the fact that both had hit
their targets successfully.

They each took a sip of water and stepped away from the displeasures
of intellect.  Too objective.  Gerard saw the writing on the wall.

Sophie, can we stay together after this?  I have a problem letting you
go.

She smiled and replied.  Yes, me too.

\bye
