\documentclass[twocolumn,12pt]{article}

\begin{document}

\title{Confessions of a Socialist}

\author{John D.H. Pritchard \thanks{jdp@syntelos.com}}

\date{\today}

\maketitle

%\tableofcontents

\begin{abstract}

Notes from here on my former r\^ole as a socio-cultural activist of
sorts.

\end{abstract}


\section{Misgivings}

It's no more than a bad habit, what I think of as my social activism.
The writers serialization of mind into a single string applied to the
idea of a walk in an overly inclusive social world.  The error in such
a thing is the inclusion of a compromise that subordinates the best
which one has to offer.  This applies to the obvious reflection, the
presidency, when politics compromises the individual.  Clearly we have
a clich\'e of a problem with Fascism, the psychology of intellectual
captivity born of socio-economic self doubt {\it cum} cultural
deficiency.  And just as clearly we have a deficiency in the knowledge
and practice of leadership.

\section{Leadership}

We know where the real expertise of leadership resides, within our
military.  We have too little appreciation for the exactitude and
proficiency and execellence to be found there.  Accepting that the
business of destruction, as I like to call it, is -- well -- unique,
(in the high abstraction of analysis) we're good at it.  And this
demonstrates qualities that are worthwhile, including our knowledge of
the mechanics of leadership.

Briefly, a good leader has power.  An educational process is necessary
to distill that into something practical.  First to learn to follow,
not only to learn to measure (otherwise humility) but also to get a
good study of that power (for those who do the work).  And then a
process of developing the practice of that power.  It's all individual
and metaphysical and therefore most of its discussion is metaphorical.

\section{Reflections}

I'm not a fan of the problems found in the socio-cultural actuality of
the United States.  From the horizon available via the
$\alpha\kappa\lambda$ sign language effort, the cultural course was
substantially moved such that production meets demand and demand is
conscious of its responsibilities to its self awareness.


%\appendix

%\section{Notes}

\end{document}
