\input preamble-pdf

\centerline{\bf Madame Selene}
\centerline{\it Thursday, 2017/04/13}

\vfill
\break

Madame Selene racks her knuckles from her seat before the crystal
ball.  Her arms in air before her intimate audiences, her palms part,
her arms extend from elbows to lift the air.  Her chin rises, eyes
close.  The crystal rises.

Eyes widen, searching sight.  Only Selene and ball are visible.  Faces
flush as pulses leap and blood sinks.  Selene has the room.

\vfill
\break

Selene catches her breath before the life runs out of her heart.  Her
chest thumps as the muscle resumes pumping.  She smells the air.  It
is cold and damp.  She opens her eye.  She sees pale moonlit faces
surrounding the sphere, glowing dimly the grey - blue color of death.
She catches her breath as her face blanches.  The realization of the
gravity of this arrival has crossed its threshold.

\vfill
\break

Those wide, blank eyes set in pale faces have ears that absorb the
sounds of air moving through buildings, over dirt gravel yards and
empty fences.  Their shock is called dissonance.  The instantaneous
discontinity in the world known to their senses captured their minds.

Selene sighs a breath of relief as no further changes have emerged in
the moment.  She rotates her palms away from her to pick up her
audience.  She sees, in this way, their state of shock.  

\vfill
\break

In this moment she is not amused by their capture.  One among them has
a psychic past that surprises her, and overwhelms the others.  She
deducts it is the space of one, solitary.  A powerful and haunted
space, but not merged with others.  No need to sort and shuffle.

She lets the moment reveal itself, taking caution on behalf of her
audience.  She relies on their state of shock to preserve their minds
while she ensures a reasonable degree of safety.  They each
understand, from rumors and news reports, that people have died in her
chamber.  Three, to be exact.  A surprise emergence in this state can
kill.  One was maimed, only to recover in hospital.

Madame, herself, has gained the experience of such explorations
through the recovery of sense following experiences of immense pain.
The mind is unprepared for the shifting realities of psychic
exploration.  The mastery of dissonance and dissociation is a lengthy
process that few are capable of.  Her most important qualification for
this work is her ability to drop everyone from their transference
automatically upon a cognitive event.

\vfill
\break

She takes a step into this space by reaching through her body with her
eye.  It remains still.  The sounds of air remain still.  

She speaks.  ``Who will open his eyes to see, and ears to hear.''

Eyes socked in pale faces begin blinking.  Her voice has reassured
them of a sense of place.  Minds emerge into the grip of dissociation.
While they do not trust their senses they are unable to open their
eye.  Some will be unable to objectify.  Most are unable to identify.

\vfill
\break

Selene has trained her sense of audience to prohibit identification.
She employs visual objectification as a cursor to health, but denies
her own identification of self or person.  In this way she maintains
the privacy of her audience.  She will not associate the experience
with the person, and while she cannot, neither can anyone else.  Their
senses are in her possession.

She becomes aware that one emerges from the dissociation into the
faculty of identification.  It is not likely to be the psychic person
of origin, but it could be.  She has no interest in deriving
information from the experience, only in safely guiding the process of
the experience.

\vfill
\break

As this one emerges into a healthier state of consciousness, Selene
recognizes a faint cacophony of electric crackling.  

The frown that covers her face is felt in the room.  A talent of
projection to provide sensory warnings and cues in the defense of
cognition.  The combined symbols of death and industry stir a sense of
nausia that she catches from her projections and shares as anger.

This causes her audience to pump adrenaline in response to the
dominant signal within their sensory reality, preparing their minds
for potential psychic emergences.

Selene focuses her eye on bodies walking through a remote mist.  She
blurs the image into view slowly for her audience, unable to protect
them from vision in an exclusive sense.  Their own minds will
accomodate the remains of her care.

\vfill
\break

They walk by, as enroute from somewhere to \break nowhere, haunted
with the numb inhumanity of starvation and deprivation.  Their heads
shaved, they are naked.  Skeletons covered in skin walking with no
more life than moving legs.  Each unique.

Selene knows of only one who can see them.  The others will recall
only having seen Selene, and as if awakening from sleep might recall a
dream.

Selene and the other wait as bodies pass by.  Each becoming more
inevitable than the previous.  

\vfill
\break

In time she concludes that this is the message, and decides to
terminate the session.  She closes her eye, and the others hunch
forward with a loss of consciousness.  A psychic sleep.

She restores the ball to the table, lowers her arms, and rests
herself.  She is exhausted.  The others need rest.  The party sits at
their chairs in the darkened chamber of her house.  

\bye
