\documentclass[12pt,twocolumn]{article}

\begin{document}

\title{Confessions of a Black White Man}

\author{John D.H. Pritchard \thanks{jdp@syntelos.com}}

\date{\today}

\maketitle

%\tableofcontents

\begin{abstract}

Barack had {\it gifted} me the internalization of my awareness of the
experience of a Black Man.  By that I am very specific.  Normally I
would respond to the assertion, ``don't call me white and I won't call
you black''.  It is not about an african complexion, skin color.  It
is historical.

\end{abstract}


\section{Rage}

With my force of spirit and intellect, the internalization of the
African American Experience as my own produced an awesome rage.  Not
against White People.  Against the History of Slavery, Civil War,
Lynchings, Civil Rights, and White Supremacy.  Against {\it Black
History}, as I call it.  And not a rage in an incivil sense.  A rage
of force of spirit.  A spiritual rage.

\section{Whiteness}

My ancestors are European, exclusively.  My experience is otherwise
technological.  The climax of history in thought and industry as from
Edinburgh or New York, in the European American Experience.  As a
``white male'' I never experienced prejudice.  I experienced no more
than the frailty of others.  In this experience I've always been
compelled to lend my strength to others when I could.  And in this
lifestyle Barack had caught me in a number of ways.  Generally, in a
sense of service that reached into a profound sense of humanity.

\section{Reflections}

The whole thing is not particularly relevant to anything excepting as
yet another source of strength and commitment to the original ``path
of the true human being'' that I've lived since birth.  

It's relevant to my relationship to Barack, however.  In that it's a
source of {\it conflict}.  It's beyond resolution of {\it what}, how
or why.  It's spiritual.  Within the individual that is me he's the
only one who understands it.  The assertion has no cause for accuracy
or precision.  It needs only represent a thing enough to be known to
his awareness, exclusively.

If he's my brother, then we fight like brothers do.  If we are to have
a relationship beyond {\it conflict}, then it will require some actual
face time.

I cannot otherwise rationalize (serialize) the thing to any other
meaning.

\section{Awakening}

Such an awakening, a spiritual opening to history, is a violent thing.
The violence is subjective and civil and unique to an extremely
particular comprehension as has no place in the public domain.


\end{document}
