\input preamble

When Sophie asked Gerard on their first date, he was a bit surprised.
He was lecturing a graduate level course on automata theory, and she
was a graduate student in physics.  She had no reason to expect that
she would accept.  Quite boldly she entered his office during the
period allocated to his students to follow up on subject material,
coursework, and related housekeeping activities.  Occasionally a
student would want to learn about his doctoral thesis, a book or paper
he'd written, or some AOS activity.  No one had ever asked him a
personal question, and at the time his personal life was generally
quiet.  The occasional meal or party with friends, especially those
events marking AOS accomplishments.  When she stepped into the room,
he recognized a graduate student of physics as one has interest in the
future.  She stood him up when she leveled a look at him and proposed
dinner.  A romantic interest.  An experiment in love binding.  He
thought for a moment, standing in front of her.  He knew how to search
his feelings.  He knew he was less than ten years older than her.
While sudden and unexpected, not unreasonable.  And with as much as a
comfortable feeling of warmth from within he accepted.  It was not the
jump off a cliff impetus that some had spoken of, but there was no
guarantee that that experience was universal.  As they discussed that
first plan he became aware of her certitude.  She was a graduate
student of physics and adept with certainty and objectivity and
subjectivity.  Her confidence opened him up like a caught fish
prepared for the pan.  And it hit him.  He flushed and took his seat.
She saw through her own hazy romantic consciousness that he had gone
blotto.  She took her seat and fell silent with the victory.  He took
a moment to find a handle.  To realize the truth of what had occurred.
He had just fallen in love.

\bye
