\input preamble

What do you think he's talking about?

He wants to know if I'm a friend.  He noticed the fight at Foggy
Bottom, and the walk to Laughing Forrest.  He's only tw years old --
he doesn't know how backward homo sapiens are with respect to their
nature -- in their problem with language and speaking.

The Hawk had set in a tree.  Jeremiah thought him a cat.  The crows
got his goat.  The crows chased the Hawk out of Foggy Bottom.  John
noticed -- and later asked Jeremiah about the Hawk.  

Jeremiah told him that they live in the Laughing Forrest, a quiet
place up the road a short walk.  John walked up to the Laughing
Forrest.  When he emerged from a brief entry the Hawk was in the trees
with the crows.  He spoke.  His baying familiar like the voice of a
cat.  His heart flies.  John looked to his sound and heard him.  

The crows played contrary.  John tipped his head as he walked before
those trees, expecting his companion could see him.  Not with them.
Friend.  

The Hawk called again.  John looked again, and thought, I am your
friend.  The Hawk replied, I am so happy -- or interested, safe and
trusting.  Yu are my friend if you say so.  It is only my feelings you
will hurt, if you betray me.  It is more than that, this trust, John
thought.  If I betray you, little one, you will turn your back on your
friends.  A heart betrayed trusts not for many years.

In this tent it gets too dark.  I open in light by folding these light
sheets.  Enough to serve this heart.  To care for my own.


\bye
