\input preamble

To use the body as telescope, bent over in the meaning of things.  The
skills to stitch together association networks and thereby to raise
the consciousness of the experience.

To study language and its origin within the body.  To study society
and its history of relationships with the body.  

The human experience is situational, social, and linguistic.  The
mathematical logic of dimensions of relationships, scales, and
languages the finest tool I've laid eyes on.  It avoids the conceit of numbers.  

Numbers count, but continuity and relativity can only be measured with
numbers.  To understand continuity and relativity is to understand the
spatial reference frame in which time and space translate and rotate.

Mass deforms the spatial reference frame space -- that is, the space
of possible locations in space - time (reference frames).

We know these locations as places and planets.  We have mass.  We rest
on planets.

In the notation of space - time, frame $\phi\ $ has space - time
attributes on the domain of reference frames.  

Locations relative to a mass and local time have these space - time
attributes on the domain of a reference frame.

In general relativity our conception of space and time expand to
include abstractions free of mass.  A free photon in space has one of
energy and mass.  The mass is a practical fiction.  The energy has
wavelength and amplitude.

Numbers prove reality to us, to each other and ourselves, by the value
of the orthogonal languages of numbers, and their logic and
disciplines.  However, they are not primary here, and neither are they
primary in much of life.  This freedom from numbers illuminates the
value of mathematical logic.

\bye
