\input preamble

Thomas returned to docks of his village with two fish that evening.
He was cold and tired, as usual.  The sea took his body in exchange
for those two fish.  This, however, was behind him as he tied off the
boat and sail and rudder and hoisted his catch onto the old wood
planks that his feet fell onto.  It was late afternoon, with an hour
of sun remaining above the horizon.  He was lifted by the modest
success he brought home.

Martin met him with his wheel barrow to fetch the catch to market.
The smile that met his son reflected the cold in his limbs and the
warmth in his chest.  He was proud to be home, proud to have won the
life his father had given to him, and looking forward to the walk
across the village to his hearth.  At this hour Anna would be putting
a fresh loaf of bread onto the table as Ruth set the table and helped
her mother prepare dinner.  He wondered if there might be a letter
from his uncle, or a new buckle from the smithy.  

As they passed the fish market Martin turned in and Thomas continued,
according to the habit that Martin had insisted upon years ago when he
first grew big enough to carry the barrow.  In the silence of that
parting his chest would swell to shake off another degree of cold and
salt.  The paving stones between the buildings rocked his feet and
legs as he passed one building and then another in his lumbering down
the street.  A butcher, a granery, a store, and then one house and
another till he reached his own door.  He opened it with the lament of
a sigh, and began the process of disrobing.  He hung one layer and
another on pegs near the door until he was free of the chore.  He
walked into the kitchen whereupon he received the acknowledgements of
wife and daughter and dropped himself into his chair at the table.
With that, his mind finally disposed until someone or something
stirred him to eat.

\bye
