\input preamble

In began in the fall of 2013 with the battle of the asteroids, the
flight of the intruder: a president, a space agency, and a global shit
storm.  The politics of the White House good for an immortal, bad for
a mortal.  That's a way to put it that covers many perspectives.  A
very large number of upset people, many really out of their minds.
Patterns in violence near and far the signs of inductive terrorism in
the collective consciousness: millions who each knew no more than it
existed.

It had emerged from the politics of money and power that had grown
into the politics of hate.  We exited the asteroid field on the
principle of a protest vote for action against the ``invisible jail
world'', and set to work on the problem of people playing with
collective nihilism without the tools to avoid self destruction.  We
put handles on the this and that of things, reminded everyone of their
common humanity.  As awareness grew a movement arose to deal with the
habitual offenders that were primarily responsible.  They were the
medium being exploited, ``the police''.  However, not all were
conscious of the fact that they were contributing to a phenomenon that
was ultimately self destructive.

For the first year I believed it was all about politics and the ``dark
matter'' thing.  I was dragged onto the stage at each step, an
implicit blanket covering my vulnerabilities.  At least that was my
view.  I can't say much more than that with a global sense of
awareness and reliability.

I know that at some point early on a love story emerged within the
chaos.  I was participating, in fact the primary driver as I was
expressing a willingness to ``move on'' in that part of my life.
Given the simplicity of the sign languages I was aware of, noise could
be something good or something bad.  Having nothing else at hand but a
demand for pages of output, I went to work on the noise.

To bring the light of self awareness -- of awareness of the facility
of the {\it homo sapien} -- into the world someone made a printing
press.  Someone made a lightbulb, an electric power grid.  Someone
made a telephone, a voice communications network.  Someone made a
digit, a transistor, a computer, and a digital communications network.

The individual is his own engineer of existence and being.  While the
the baby wants to sit and cry and wait to be picked up, the adult
needs to learn how to hold itself, to lift and carry and develop and
realize the self.  We can dream of a partnership that does this like a
psycho-emotional ping-pong, but interaction depends on handles.  The
self needs the handles one develops for oneself, and a relationship
needs handle balance.  The person who doesn't know how to care for the
self can't be helped by others.

\bye
