\input preamble

Some people have nothing better to do than to cause pain -- or try to
cause pain -- for others.  Shades of ass.  I remember a documentary
that recorded some of these lows and the display of asses that stood
in silence.   

It has a spectrum that reaches well into evil when realized as a force
against humanity.  This had been the experience of the world over the
course of the past twenty years in particular.  At least I'm not aware
of a broad, street level movement against conscience that believes
itself to possess a superior consciousness to all others.  But I've
not studied it.  I'm simply aware that it exists.  I've watched
individuals turn on each other in the spirit of the thing, with the
faculties of the pattern.  Economic attrition.  Creating a sustained
environment for mental stress.  Playing with random messages in sign
languages.  ``Get the message''.  As if there was something to be
understood.  It's ass.  ``Smells like ass''.  No more sensible than a
natural randomness that pulls on curiosity.

Having watched it long enough, it becomes evident that the psychology
of this phenomenon is rooted in the projection of self deficit onto
others lacking at least the appearance of psychological self deficit.
No more than ``they're not cool'' in this negative sense.

In the global perspective the movement has been exploited and
manipulated by those seeking power.  A ``southern strategy''.  Some
years ago there were train wrecks and car accidents that clearly
occured within a pattern of coordination and control against humanity
and government.  No more than hegemony seeking power.

For this reason I started calling it by the terms ``evil'' and ``the
whore''.  It came out of no where, out of the dark, and was plainly
lacking in merit of any kind.  There was no facade, no speech.  There
was a sublimation associated with it that smelled of exploitation and
control and destruction and so it resonated with the aberrant and the
abnormal.  Hence ``the whore''.

The political dimension is just as dark, although by now it is well
known under the rubric ``black block'' and ``dark money'', and this
dimension of the subject is readily researched online.  

It surprises me that the popular facility of evil is so rarely
mentioned.  Here's a mention.

\bye
