\input preamble

He knew where it was, the interior of his heart, and how to bring it
out to project its force.  But she believed it a place of mind, or if
not that relatively superficial thing, then she saw the pain he was in
while bearing it so.  For two years he bore a breast that had no place
in her world, that part of her world she needed to persevere.  The
conflict between them manifest within him as torture.  When finally
their communications and interactions had it identified and
characterized, they put it away.

It was many hours of relief and observation before he was ready to sit
up, again, and take notice of what had occurred.  That he had brought
the interior into the world.  It could be suggested that the effort
had represented inexperience or inadequacy, but deprecations and
depreciations could not measure it.  It was the lion's heart, untamed
and unbroken.  And then much more than that.  The source of character
and emotion and devotion had been stirred.  A fault could be found in
the need to project that, but lacking the skills of art to project
himself adequately, he concluded that the force of youth was necessary
and appropriate to the challenges he faced.

What a strange thing, their elected marriage.  So much pleasure and
pain.  So much patience and impatience.  Married because they said so,
there could be no finer thing in his estimation.  The courage of it
worthy of his heart.  He expected her courage, their courage to bring
them together as by magic.  She would appear before him, in his local
frame.  It would be.

Not a place of mind or illusion of heart, the product of a great deal
of love over a great deal of time.  The time of a thousand days.  It
was enough.  Life is short.  They knew better than to waste time.

We pass this way but once.  I dream of love realized in actuality.
Understood.  Comprehended.  Shared and returned.  For if not, then
not to have made use of this life.

\bye
