\input shorts

{\title Political criminology}

{\date Saturday, 10 July 2021}

{\section Anarchy}

\bigskip

The principal effect of the political intercourse with criminal
exploitation would be the legislative act.  And the principal effect
of the sociopathological adversary would be the distrust, dischord,
and division that dilutes the practice of law, generally.

This is what we see, from innumerable perspectives.  Tiled across the
experience of actuality like the stars of the galaxy.  Polluting the
experience of reality like the rains of Spring.

Realizing sociopathology to be educational failure, the
criminalization of anarchy is practical.  Conservative of humanity.
Divesting of inhumanity.  And recognizing of the necessity of not
being subjugated by the unwilling and incapable.  Which is a
deterministic alternative choice set.  Order of sanity over conflict
of insanity.  Or the inverse.  Where humanity fails, inhumanity
expands.  One must dominate because one will dominate.

The humanist ideal becomes educational on average over the long term.
This is what we see.  The arc of history has brought us to a highly
organized state.  We have walked on the Moon.  We have robots on and
orbiting the inner solar system bodies.  Doing science.  We have
instantaneous global broadband communication.  Utility and
productivity over body are enormous.  We find ourselves very far away
from a primal existence.  The difficulty is in teaching and learning
about the primal existence found in the educational failure.
Developing that material of information has not obviated or negated
the anarchist.  We find ourselves not invested in alternative
solutions.  First, the general awareness and priority of the general
population must shift away from self service to accept public service
as necessary to wellbeing and welfare.  This fact of necessity follows
from the compromising effects of political crime, and complements
awareness generally.  Both law enforcement and psychology have failed
to solve the problem of sociopathy.  Everyone must reorient from
defense of person by independence to defense of person and society by
interdependence in social maturity of person.  The educational
failures are dependent children criminals who perform use and take
continuously throughout life.  That presence requires perpetual
awareness in person as well as every aspect of life up to and
including politics.

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
