\input shorts

{\title Logical existentialism}

{\date Thursday, 24 June 2021}

{\section Metaphysical reference frame system}

\bigskip

The formal type system established in [2021/06/17 Journal 0], and
developed in [2021/06/23 Journal 0] is metaphysical.  The degree of
abstraction challenges the logical tradition when replication, and
therefore semantic stability and representational coherence, are
uncertain.  In metaphysics we must be able to represent any
experiential observable including the imaginary and relatively
imaginary, as well as the esoterica of experience and learning
unestablished in thought by recognition of reflection or condensation
of language.  We must accept a trustworthy account as worthwhile,
prepared to discover the fact of it.  The observable is relatively
physical when the experience is sensory.  The obserable is relatively
metaphysical when the experience is imaginary.

The phenomenology of transience and persistence is not or probably
reproducible.  The transient case is relatively metaphysical, and the
persistent case is relatively physical.  In the study of transient
phenomena we have no use of the concept of error.  While in the study
of persistent phenomena we may validate by replication and thereby
expand our interests to include independence and error.

With the intrinsic frame,
$$
 \phi \, [ \, \omega \rightarrow_{\rho} o ] ,
$$
we handle transient phenomena and abstract concepts.  The analogy to a
dictionary is abstract.  The representation of sentience is
phenomenological.  When we find a dictionary error, we update the
dictionary.  The intrinsic frame is available to represent the
processes of experience, learning, study, research, and development,
while the extrinsic frame is familiar to scientific and industrial
processes.

With the extrinsic frame,
$$
 \phi \, [ \, \omega \rightarrow_{\rho} \mu + \varepsilon ] ,
$$
we model and validate.  When model ($\mu$) and error ($\varepsilon$)
are independent, the validation by replication holds.  In the process
of developing the model, the complexity of the model is expanded into
comprehension until the error is independent noise.

The physical variant has been named the scientific method, and
formalized in measurement theory and statistics.  The metaphysical
variant warrants greater understanding, familiarity, and
comprehension.  The communication of observation would begin with
formal framing.  A hallucination may be shared as an experience of
unknown physicality.

Likewise, gaslighting in ambient atmospheric noise is tedious to
represent.  And, that dependent inanity might readily overwhelm the
social presence required to recognize the representation of obscure or
violent experience.  In the development of framing and observation,
further experience yields greater awareness.

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
