\input shorts

{\title Logical existentialism}

{\date Friday, 19 February 2021}

{\section A logical psychological morality}

\body

The physio- cognitive morality is a metaphysical fabric of will and
representation (established in {\sl A logical existential
experientialism} of {\sl 2021/02/18}).  The space of gross moral
classes includes the four cardinals identified in {\sl A logical
psychological morality} of {\sl 2021/02/15} (and updated {\sl
2021/02/16}).

It would be natural to recognize metaphysical morality as
nondeterministic and nonlinear.  Derived metaphysical facts are fuzzy
due to the complexity of the individual interior.  This note
reinforces and develops that understanding.

The metaphysical moral ontology demands qualification.  An alternative
ontology is superior in the greater abstraction of half as many
degrees of freedom.  The dichotomoy {\it creative} and {\it
destructive} envelops the space of possible moral fabrics.  As
qualifiers, the {\it angelic} type class produces {\it creative
angelic} and {\it destructive angelic} derivatives.  The former is the
evident redundant equivalent, and the latter is a region intersecting
(self) constructive and destructive metaphysical fabrics.

An interpretative case is physically self destructive and
metaphysically self constructive.

The possibility space of the moral fabric of the metaphysical manifold
is enormous.  Most cases are gray and relativistic.  The cardinality
of the ontology is misleading when perceived as rigid and
deterministic, because the actual domain of examination and the object
of representation is nondeterministic as well as nonlinear.


{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
