\input shorts

{\title Logical existentialism}

{\date Wednesday, 3 March 2021}

{\section Existential sovereignty}

\body

When the sovereignty of humanity is an assertion of rights of
individual and social independence, the violation of those rights
becomes equivalent to the betrayal of those rights {\it (by
abstraction to humanity)}\/.

In the abstraction there is negation.  And at this degree of
abstraction, humanity, a failure to assert rights has equivalence to a
failure to support rights.

This frame of reference is the {\bf law of sovereignty}.  In the frame
of sovereign rights, the term {\it law}\/ has equivalence to the term
{\it rights}\/.  ({\it E.g. C'est la droit.}\/ Humanity has
equivalence to to sentience, and relation to metaphysical maturity.
Being is well or ill, and has relation to metaphysical and physical
externalities.  In terms of classical law, the frame of human rights
is the theory of law.

A dramatic and relevant first most salient case of analysis is a
disassembly of the term {\it prostitution}\/.  To begin we recognize
the syntactic and semantic object as volatile and archaic.  This is
analytically causal to analysis.  Is the term abusive?  Of course it
is.  The typical employment is a violation of human rights.

The term is employed as a sadomasochistic term of art.  However the
sex worker is challenged, the ``prostitution of body'' as may trade
wellbeing for illbeing, is none other than contradistinctual to a
practicable legal term of art.  It is a sexual allusion to a political
crisis {\it (of education)}\/.  Because the trade of sovereignty for
ignorance or insecurity occurs at the humanity milliennia length
scale, it is unknown until uncovered.

Political prostitution occurs at the trade of sovereignty for
subjugation.  It is a prostitution of person to ignorance which we
must recognize as a social obligation of responsibility.

Generally we entrust ourselves causally.  We are born, grow, mature,
and perish.  The causal origin is familial and social.  The
responsibilities to person innure to family and society.  Nonetheless,
we are metaphysical as well.  The educational endowment required of
person and society is manifest from an effort of development on behalf
of both individual and society {\it (inclusive)}\/.  The metaphysical
origin of maturity is regarded as largely individual because it is an
enormous time sink.  The prioritization of reading and writing is
challenged by the same awareness that demands it.  That causal paradox
is trap and salvation.  And, indeed, awareness is the maturity of
sentience and acuity that determines individual wellbeing and welfare.
Unfortunately, the critical role of language is far too often ignored.

Following, legal remedies improve wellbeing and wellfare.  And this
temporal logic affords the practical and theoretical existence of
government as the institutionalization of the practice of law.
Practical law of government is therefore distilled from the theory of
sovereignty {\it (or existence)}\/ as the sustenance of the public
good.  And therefore the moral fabric of being is sustential {\it
(again)}\/.  The false morality of politically popular convenience is
prostitution.  

{\tail John Pritchard, @syntelos [CC-BY-NC]}


\bye
