\input shorts

{\title Sociopathology}

{\date Tuesday, 6 July 2021}

{\section Definition}

\bigskip

The fundamental property of the sociopathological observable is
objectification.  The objectification of other is the {\it
kindergarten failure} where individual has failed to acquire the
conception of society as a membership inclusive of self.  Has failed
to place self and person into world as equal among others.  Remains
immersed in the neonatal cognitive universe as a unique isolated
sentience absent cognizance as open to experience.  What we identify
as the cognitive strategy of awareness: the perpetual acquisition of
the actuality of condition, situation, other, group, world, and
universe.

The classical sociopathological condition has a degree of subjugation
of the perceptual {\it object other}.  The {\it subject object}
contrasts to a healthy {\it person object} of a physical observable or
relationship in $\alpha\phi\tau$\/.  The person is the social presence
or presentation as presents or measures expression or behavior in
time.  The perceptual {\it person object} affords the modest and
constrained conflict of cognitive conceptual development by
communication.  In contrast, the {\it subject object} has a deficit of
compassion expected of cognition and required of intercourse.  The
ultimate respect for the understandings and misunderstandings that
form cognitive sharing of information by communication is due to
compassion.  The {\it person object} may not represent a relationship
as demands social maturity.  The social facility is implicit in the
communication that shares a cognitive contact for the purpose of
information sharing.

The sociopathological condition is marginal where the social {\it
person object} may or may not be proprietary.  Self awareness may
recognize and restrain the error of impropriety in which one would
effect propriety over another.  For example, by the violation of the
propriety of another by associations to skin color.  Self awareness
fails at the suggestion that the error of impropriety is endangered by
the mass extinction of general social ignorance.  By condition of
inferiority or situation of insecurity, the suggestion that the
imaginary power of inanity threatens self and person is destructive of
the cognitive strategy of awareness and moral fabric of being.
Priorities revert to biological from cognitive necessities by terror.

\bigskip

{\section References}

\bigskip

{\ninerm [2021/06/14 Journal 0] Political narcissism}

{\ninerm [2021/06/27 Journal 0] Logical existentialism}

{\ninerm [2021/07/03 Journal 0] Political criminology}

{\ninerm [2021/07/04 Journal 0] Political criminology}

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
