\input shorts

{\title Logical existentialism}

{\date Monday, 29 March 2021}

{\section Conservation of sovereignty}

\bigskip

The effectual distinction of existence from subsistence is necessity
from foolishness.  Any animated effect has this distinction of {\it
anima} and {\it animus}\/.  And from effect we have cause as intent or
(relative) accident.  This accident is an abstraction over {\it
animus}\/.  It is culpable.

When we recognize the matrix of effect as make and give {\it versus}
use and take, we characterize the {\it anima versus animus}
distinction.

The law of sovereignty is conservative of existence, to displace
subsistence and nihsistence.  It is necessary to the conservation of
our sustenance, wellbeing, and welfare that we educate and maintain
awareness as conservative of life.

The {\it anima} of existence and necessity is the awareness of
perceptual aptitude and effectual capacity.  With the education of
physical and metaphysical awareness is socio-economic security.
Awareness is conservative of body, person, and self.

This existence as superior to subsistence and nihsistence is
comprehensive of {\it anima} and consciousness.  The effect of
wellbeing is intentional as awareness provides for wellbeing.

In all matters of substance to self and person, metaphysical wellbeing
is presumed, required, or critical.  Analogously, the society of group
or nation if effected existentially.  Is realized by intent or
accident.  And by accident is self destructive.

The conservation of our sustenance is the conservation of our sanity.
When we open the perspective to comprehend the nondeterministic and
nonlinear complexity of our metaphysics, we confront apathy, sympathy,
and empathy as psychopathy and emotion.  We employ the matrix of
effect to resolve intent in terms of state of being as existential and
healthy, subsistential and functional, or nihsistential and
dysfunctional.  Or healthy and necessary, or unhealthy and foolish.
Innocent or culpable.

{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
