\input shorts

{\title Logical existentialism}

{\minor \line{\hfill Friday, 5 February 2021}}

{\section A logical psychology of authority}

\body

A crisis of authority is an expression of subsistential crisis.

A psychological subsistence finds

$$
 ( \psi = {\alpha}/{\iota} ) < 1 .
$$

A psychological dilemma occurs where
$$
{\phi}[({\alpha}/{\iota}) > 1]
$$
conflicts with
$$
{\phi}[({\alpha}/{\iota}) < 1] 
$$
for a frame of reference, ${\phi}$.

This is common to issues of authority.  Assertions and appearances of
authority conflict with rationalization of realism.  The realism 
$$
{\phi}[{\rho}] \longleftarrow {\phi}[{\gamma+\pi}] 
$$
requires authority.  The rationalization demands authority.

A psychological subsistence is uncertain of a world order
$({\phi}[{\rho}])$ relative to horizons of social inference and
physical mortality $({\phi}[{\gamma+\pi}])$.  The subsistential crisis
appears as confusion and aggression.  Conversely, patience and
reflection are employed to resolve experience to understanding.

The issues of authority illuminate a copndition of
hyper-rationalization.  Reality is not manifest, it is decided.  And
the decider is me.  The decider must be me, because I need a reality.
Reality as a tool of exploitation has produced reality as the subject
of manipulation.

A standard of observational reality would find
$$
 ({\psi} = {\alpha}/{\iota}) > 1 . 
$$
While a standard of false reality finds
$$
 ({\psi} = {\alpha}/{\iota}) < 1 . 
$$
Awareness is psychologically less significant than insecurity.

These issues in subjective realism are distinct from issues in
objective realism as confront physio-social authority.  The authority
delegrated to law enforcement officials by government and law
confronts the issues of subjective - objective dilemma regularly and
repeatedly.  At any moment, the network of subjective and objective
facts and figures facing an issue of interest or concern exhausts
comprehension.  That practice is existential when it resolves
recognition and identification, and develops understanding and
description, in a reproducible discipline of conduct.

\bigskip

{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
