\input shorts

{\title Political criminology}

{\date Sunday, 4 July 2021}

{\section Literacy, logic, error, and propriety}

\bigskip

{\ninerm

  {\hfill \nineit ``Stealing money.}

  {\hfill \nineit ``Feeling time.''}

  \smallskip

  {\hfill {\ninesl Johnny Utah}}
}

\bigskip
\bigskip

In my experience it was Newt Gingrich who developed the exploitation
of C-SPAN to the normalization of error, inanity, polarisation, and
{\bf sociopathology}.  The violation of logic became increasingly
popular, and politics became a pleasure zone, an echo chamber.  The
race to the bottom started there, and was established with W. Bush.
The prevalence of inanity at the concentration of our power is
irrational.  The effect is imaginary.  The effect is metaphysical.

The phenomena of fascism include insecurity, fear, and sociopathology.
We could encompass the observable with an expansion of Sociopathology
to include natural and artificial spectra.  The natural range is
classical.  The artificial range is marginal and affected.  The {\it
social violation power} normalizes classical and marginal
sociopathology, which is an effect of disturbance, fear, and terror.
The abandonment of logic is an abandonment of literacy, and an
invitation to the violence of self destruction.  The absurdity of
insanity is terrifying.  The inane effect is relatively
sociopathological because it is reinforcing, and because this is the
fascist effect.  This affected victim, the sociopathological xombie,
was unable or unwilling to reject the invitation to the imaginary
power of impropriety.

The unaffected are protected by their adherence to the cognitive
strategy of awareness.  The patience to witness the manifestation of
actuality in time.  The practice yields a moral fabric of being that
rejects self annihilation.  In awareness one sees errors, and self
preservation is expressed constructively.

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
