\input shorts

{\title Logical existentialism}

{\date Sunday, 27 June 2021}

{\section Sociology \& Sociopathology}

\bigskip

When the individual conceives of society as informal, a membership of
subtle body $\alpha\phi\lambda$\/, relationships have no requirement
for formality.  When the individual conceives of society as formal, a
membership of physical body $\alpha\phi\tau$\/, relationships have
individual requirements for formality.  Preservation of self is
maintained by effects of distance and propriety.

The conception of society may be esoteric.  The distinction has
equivalence to awareness when the individual does not reject social
formality.

The premise thus developed is not practical, which experience previews
the necessary derivation to (a) rationalism (of awareness).  However,
it remains the relevant, common, and popular contest for the
resolution of the acceptance of criminalization in society.  The
anarchist proposition that freedom be inclusive.  That devices of
government are exclusionary.

Perhaps the term democrat or socialist may best represent freedom as
social independence and economic interdependence as individually
proprietary, with government established to serve the common
sustenance and development as a public goods industry in law and
education.

Therefore the anarchist position compromises individual to society.
The other imposition is a tolerable time sink.  Life is thus occupied.
The limits of intention are discovered arbitrarily, and may be
resolved by violence.

Generally, self preservation is subsumed by society and we regress by
millennia.  At least in terms of productivity and reproductive
freedom.  One imagines that the males kill off their compeitors and
the females bear children.  When the principle of existence is
reproductive, and individual is subsumed to society thusly, rape is
sex and murder is its partner.

Our evolutions over our millennia have rejected anarchy as
impractical.  Intolerable.  We develop and sustain the rational
outcome in social independence and economic interdependence as
individually propriety.  And we recognize that the essential device of
derivation is awareness.  This we identify as humanity.  In society,
the sovereignty of humanity.

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
