\input shorts

{\title Political criminology}

{\date Saturday, 26 June 2021}

{\section Definition}

\bigskip

Perhaps political criminology is distinguished from political warfare
by membership, rather than believing that ``political warfare'' is an
error of conception.  Certainly the distinction is critical.  When
Putin's Russia attacks the United States government in the
manipulation of social reality through disinformation, it is a crime
against humanity as a metaphysical terror campaign.  When Republican
political polarization attacks the United States government in the
manipulation of social reality through disinformation, it is likewise
a crime against humanity as a metaphysical terror campaign.  The
experience of these campaigns is one of either foolishness or
disturbing.  Which is a practical and effective and increasingly well
known cloak of invisibility.

In the case of Russian terror, the most heinous evidence appears in
domestic policing and judiciary.  In the case of U.S. domestic
political terror, the most significant evidence may be that which
appears in media.  If entities like DHS and FBI are performing
``dogging'' and ``needling'' harassment via twitter, the significance
of those crimes is large.  If entities like Senators and
Representatives are likewise performing ``dogging'' and ``needling''
harassment via media, the significance of those crimes is large.  And
the expectation of the recognition of current actuality is the
conclusion that these concepts are available to assertion as fact.

In both the United States and Russia, and similar evidence is apparent
from China and elsewhere, political violence has metaphysical and
physical forms which have been criminalized in law.  Therefore, if we
are to respect the law as members of sovereign humanity, then we must
assert and support the sovereignty of humanity by recognizing the
criminality of political terror and excavating the foolishness
exploited by the criminal intent to compromise the law.

Ideally, our laws have been legislated to assert and support the {\sl
sovereignty of humanity} as founded upon individual wellbeing and
welfare in human rights.  This is the establishment of the United
States found in the {\sl Declaration of Independence}\/, and this is
the existential principle common to the planetary population.  That
criminalization exists to assert and support the sovereignty of
humanity.  Its manipulation in the psychological diseases of delusion
is the object of compassion, not the criminal and not his crimes.

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
