\input shorts

{\title Logical existentialism}

{\date Tuesday, 15 June 2021}

{\section Metaphysical reference frame system}

\bigskip

Combined,
$$
{\alpha\phi\tau}\atop{\displaystyle{\alpha\phi\lambda}\atop\displaystyle{\sigma\phi\tau}} 
$$
the {\it metaphysical reference frame system} [2021/06/14 1]
comprehends intimacy, familiarity, and formality.  Instant, moment,
history, and eternity.  Tranquility, peace, civility, and violence.
Advancement and regression.  Development and destruction.  In cause
and effect.  From within and without.  It is our humanity and
inhumanity in objective.

The practice of comprehension requires orientation so that the issues
of opacity of substance and transparency of representation have matter
of relevance and convenience, recognition and understanding,
consistency and continuity.  This effort is proposed in advancement of
our facility of objective.

The problem solved envelops the mathematical type theory.  The logical
primitive object is defined and employed as frame, observable, and
association.  Any psycho -- physiological object of recognition,
experiential or abstract, is an observable.  With appearance the
observable becomes an object of recognition in a frame of association.
With some recognition there is some association of recognition which
is an observable object.  The metaphysical analogue to the logical
primitive object is a mathematical type.  The equivalence is
illuminating.  That experiential logic and abstract logic have
some commonality is elementary.  

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
