\input shorts

{\title memoir}

{\date Friday, 9 July 2021}

\bigskip

It will be eight years in September.  The odyssey through Asheville
that originated on Maryland's Eastern Shore at Wallop's Island has
been an epoch reinvention.  The processes of adoption and adaptation
have been dramatic.  The issues of media and society.  The issues of
government and law.  Entering into world society.  Developing a
facility with the anthropo-linguistic ideography of the planetary
optical partnership.  Developing a facility with the ground effects of
a tangency to the planetary optical partnership.  Keeping faith in
humanity.  Maintaining the development of research necessary to the
sustenance of innumerable relationships.  With a week in Asbury Park
(New Jersey) arrives a sense of social maturity.  Understanding and
comprehension.  The world population remains in catch up mode, many
have yet to enter into a sobriety of awareness with the material in
government.

I like to call it political narcissism, but it might be better
represented as political crime, or sociopathological politics, or
sadopopulism.  Certainly political crime is most immediate,
purposeful, useful, comprehensive, and practical.  The remainder is
background which presents aspects of comprehension.

In this place there is both my awareness of what goes on, and the
actuality of what comes next.  In New Jersey we are quick to recognize
nonsense and to escape the clutches of intimidation ({\it e.g.}
extortion) and isolation ({\it e.g.} blame the victim).  In contrast
it goes slowly in The South where the inane bark and cry until their
sympathy is won, water is carried, and the pride of day meets the
cause of patriarchical potency.  Technically, the Culture of Violence
is a criminal conspiracy, but that oligarchy is so old that the
hegemon is an emperor.

The perspective evokes the conception of the post trump world as the
deep recovery of humanity from such apathy of inhumanity.  Returning
to the arc of history by perspective on our abuse and terror.  With
perspective of experience and learning the dictator looks foolish.
And we remember when his minions declared experience inane and
learning foolish.  With the recognition that inanity is real and
common and anarchical and viciously self serving, we recognize the
need to make space for sanity.  To maintain the presence of patience
to realize the voice of reason.  To share information rather than
larceny and felony.

This evening has been witness to an unnamed tropical storm.  And this
morning from 0445h to 0515h we were warned of a tornado possibility.

Police Officer Griffiths introduced himself with remarkable calm,
patience, and care.  He recommended Doug Shultz at the Mission as a
housing counselor with extraordinary skills.  ``MAGIC''.  I do hope to
relieve myself of the tedium before winter in New Jersey.  Or another
storm.  Which is easy enough in immediate terms but not very
practical.

On the whole, the situation on the ground is familiar as the
prevalence and manipulation of betrayal.  Altitude above ground might
be known by frequency and probability.  The ``dog eat dog'' or ``rat
race'' pattern concepts represent education overwhelmed by chaos,
competition, and conflict.  The languages of violence.  The
annihilation of self.

The sociopathological population entertains itself, formulating one
extortion after another unless deterred from aberrant behavior by
society.  The convenience of anarchy serves crime in politics.  The
suggestions that greed is good, jealousy and cynicism are pragmatic,
division and conflict are welcome, have ears to indulge in the
sociopathological spectrum.  Rather than utility and productivity, the
political criminal serves chaos and anarchy because they distract
society and empower criminality.  The collaboration of sociopathology
has the character of camouflage, entertainment, and fool-buggery
because it is none other than these behaviors.  But yet we permit
insanity to displace sanity when we fail to assert and support
humanity.  The effects of harm thus permitted are enjoyed and rewarded
within chaos and conflict.  And that propagates.  Pleasure due to harm
resonates within the sociopathological spectrum, otherwise
disturbance, fear, and terror.

Knowing that the educational failure is sociopathological, we know the
boundaries and shape of that effect.  We are thus prepared to survey
and review the sociopathology of betrayal, including frustration and
animosity.  In the macrocosm we are all members of an affected
society.  There is no independence from the compromises to our myriad
possibilities.  Those possibilities that seem to lie beyond our
political practicality.  Those possibilities that seem to abandon
aspiration to labor.

Experience suggests that there is a conversation to he developed in
political pragmatism.  If the representation relationship is found to
be in justification of political crime, then that political pragmatism
stands in error of propriety.

The effect of the political gerrymandering would develop
sociopathology and criminality.  Would effect fascism.  This is the
exploitation function, and the problem is avaricious self service in
politics.  While the sociopathological gerrymandering is criminal, the
enterprise is likewise criminal.  We must choose a pragmatism that
upholds the rule of law.  This outlaw territory is causal to our
terror concern.  The criminality must be redressed so that
representation is not unlawful.

\bigskip
{\hfill {\ninesl John Pritchard}}

{\hfill {\ninesl Asbury Park, NJ}}

\bye
