\input shorts

{\title Logical existentialism}

{\date Saturday, 12 June 2021}

{\section Individual metaphysical reference frame}

\bigskip

The individual metaphysical reference frame 
$\alpha\phi\lambda$\/,
$$
 \alpha_{\phi} = \kappa_{\phi} + \psi_{\phi} + \delta_{\phi} + \lambda_{\phi} ,
$$
is proposed as not physical without time.  [2021/06/09 Journal 0 and
1]

The nondeterminism of the metaphysical individual is found at most
length scales.  We can perform deterministicly in special, purposeful
contexts, but are generally nondeterministic.  The metaphysical
situation is fairly represented as a quantum mechanical manifestation
of the neurology, or the couple of learning and performance is
constructive of an unknown future on any relevant length scale.
Temporal linearity is available to physicality ($\delta$), but
determinism is not a principal component.

The individual as conceived, here, is strongly related to language.
The meaning of linguistic expressions are found by individuals.
$$
 \lambda_{\phi} \longrightarrow \alpha_{\phi} 
$$
The availability of information to intercourse is the principal
individual empowerment.  The communication of awareness establishes
and expands individual horizons, and is the principal social
empowerment.    
$$
 \lambda_{\tau} \longleftrightarrow \alpha_{\tau} 
$$
This individual has invented and employed language to enhance
existence by performance.  Language is the critical feature of
metaphysicality.  The $\alpha\phi\lambda$ is available to
interpretation as the expression of metaphysicality.  The metaphysical
individual is sentient ($\kappa$), conscious ($\psi$), mortal
($\delta$), and linguistic ($\lambda$).

However, $\alpha\phi\tau$\/, in contrast to $\alpha\phi\lambda$\/,
might suggest the violation of temporal incompleteness.  The processes
of reflection require an evolution of thought in time.  Reflection is
not immediate, and cannot occur immediately.  The metaphysical
recognition requires or implies elapsed time.  The temporal
observables available to $\alpha\phi\lambda$ exist as nonlinear and
nondeterministic.  In contrast, $\alpha\phi\tau$ suggests temporal
linearity and determinism are relevant.  

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
