\input shorts

{\title memoir}

{\date Friday, 9 July 2021}

\bigskip

It occurs to me as odd that speech is not as highly valued as I had
believed.  Through this journey the nigger morality of jealousy and
cynicism has figured larger in presence than I would like to believe.
The foolishness that begs expression by violence, confusion, and doubt
has virtually continuous daily presence around me.  I've learned by
experience that it is a variation on the theme of fascism.
Resonsances within the sociopathological spectrum.  The entanglement
of ego, the spirituo-linguistic trauma of violence.

Unfortunately, that mindlessness is political prostitution.  Humanity
is insulted, and by that the sovereignty of humanity is degraded.  One
gives oneself to bondage of slavery in exchange for a lash to the
posterior of cognition.

The material of society as currency of status is lost to the
alternative sovereignty of subjugation.  There can be no doubt that
senseless monarchs, oligarchs, and would be emperors are supportive
and demanding of such larceny and felony.

To say that speech is vital should resound within louder than
reproduction but quieter than nourishment.  Understanding the
significance of communication to individual and society should be
foundational to adolesence.  Understanding the restriction of speech
is foundational to politics.  Differentiating the conservative from
the criminal is critical to the stewardship of society that each is
obligated to.  The vulnerability of government to avarice is in
evidence around the world as in every tile, brick, and plank of every
floor on the planet.  Exhaustive is the volume.

Conversely the rage against the political class conflict and the
cultivation of frustration and animosity central to the chaos and
conflict demanded by the political criminal enterprise.

The conclusion that sociopathology is an educational failure is
surprising, and would explain my worst experiences and their
frequency.  The presence of phenomena of violence and conflict demands
resolution.  The character of expression as related to my person is
independent.  The majority favor self preservation, and an
infinitesimal minority are self destructive (in the blue states).
That is the production of political class conflict.  More evident in
the red states.

Time and again I am witness to the attempts to encourage chaos and
conflict to harassment.  The sociopathological spectrum is wary of
that which normally opposes.  The imposition.

That speech should invite animosity is coincidental, in one
perspective.  The occurance of presence is the occasion of incidence.

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
