\input shorts

{\title Logical existentialism}

{\date Tuesday, 8 June 2021}

{\section Political class conflict}

\bigskip

It is criminal to exploit violence in the pursuits of the larceny of
extortion but we see it at high frequency due to the blinding and
desensitizing effects of violence.  This cycle has become the {\it
modus operandi} of daily life for many who have no greater concern
than to effect any exploitation regardless of the considerations and
laws of society.

The distinctions of violence are simple.  The differentiation of
intent is an examination of the self evident.  The dissuasion of
objective by violence effectively obviates criminality, promoting the
ease of benefit of larceny and felony.

The prevalence of larceny and felony in government and industry is
amplified by the political class conflict produced by exploitation
media and politics.

This metaphysical violence appears as an ubiquitous culture of fear to
those submerged by the gravity of the experience.  And it is amplified
and propagated by errors of objective induced by errors of conception.

In the United States there is one class of person, the human being.
The class hierarchies of our ancient and medieval history divide the
sovereignty of humanity and the efficacy of society.  Our laws in
theory and application conserve life as humanity in the conservation
of the society and environment that sustain us.

It is the necessity of this existence that we respect society and
environment in order that we have something tomorrow as well as
yesterday and today.  In order that we not destroy our own children by
accident or purpose, directly or indirectly.

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
