\input shorts

{\title Logical existentialism}

{\date Saturday, 5 June 2021}

{\section Physical socialism}

\bigskip

The term {\it physical socialism} has been introduced in [2021/06/03
Journal 1] to represent the national political concentration of power
in law, economy, population, and time.  In [2021/06/04 Journal 1] it
is developed under the rubric {\it global social reference frame} or
{\it physical society}.
$$
 \sigma_{\phi} = \pi_{\phi} + \lambda_{\phi} + \gamma_{\phi} + \rho_{\phi} + \tau_{\phi}
$$
Issues of government and economy may be found to be temporal processes
of development and evolution over population ($\pi$), law ($\lambda$),
government ($\gamma$), and economy ($\rho$).

In this frame, {\it physical socialism} contrasts to {\it physical
capitalism} as the nation is politically sovereign or subjugated
[Metaphysical review 2021/06/03 Journal 0] [Physical socialism
2021/06/03 Journal 1].

Issues of subjugation can be subtle.  The differentiation of
conceptual subscription in mutual benefit of national interest, and
political subjugation in a relatively exclusive benefit of interest,
can be remote and tedious.  Social reality is commonly accepted as
wisdom.  However, social reality can be rubbish.  Exploitation media
spans sex and politics.  The exercise, discussion, description, and
study of our national collective will is dissuaged and discouraged by
the heart of darkness.  The exploitation of social reality by benefit
of popular response is common to the issues of national politics.

To annihilate the concentration of our political and economic power,
thusly, is an obvious crime against our collective health and
wellbeing.  It is necessary to become familiar with the issues of
power.  It is a variation on the themes of social independence and
economic interdependence.  

\bigskip
{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
