\input shorts

{\title Logical existentialism}

{\date Thursday, 18 February 2021}

{\section A logical existential experientialism}

\body

If the universe of each individual is subjective, the objective is
discerned by will of spirit and the logic of representational reason.
The acuity of awareness has physio- experiential and logico-
conceptual aspects.  The logico- existential conception of awareness
as objective serves individual development while ignoring or delaying
the recognition of physio- experiential awareness.  In the
experiential frame of reference, an existential morality typically
confronts subsistential morality on occasion.  To recognize intent one
may perform a familiar interpretation.  The mountains of will and
representation are scaled many times daily.

These transformations of that perceptual frustrum include the
complexity of the physio- cognitive system of consciousness, and the
complexity of the cognito- moral system of psychology.  These two
major state systems evolve spiritually and experientially.  The
handling of self is spiritual, and the universal immersion is
experiential.

Once the subjective is distinct from the objective in conception and
experience, and the characterization envelops spirit and intellect,
the ancient supremacisms of the scholarly disciplines gives way to the
nature of self and being.  And the individual instrument is divorced
from the ancient supremacisms of artificial economic wealth.

{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
